On The Impact of Atoms of Confusion in JavaScript Code

### 2022-07-25 3_Method.tex
small fixes in the text

\castor{We must have introduced the atoms before.}
The first experiment we perform uses a repeated measures, or within-subject, design~\cite{Keselman:2001:ARM}. This experiment is inspired by the work of Gopstein et. al~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, but targeting JavaScript instead of the C language, and including some methodological differences. It covers all the atom candidates analyzed in the work of Gopstein et al. that can be transposed to JavaScript and adds candidates that are specific to JavaScript. Overall, we select 24 atom candidates in the repeated measures study.

@@

The design of the repeated measures study considers two treatments: the presence or absence of atom candidates within the programs. To identify atom candidates, we start out by selecting every atom candidate from Gopstein's study that can also happen in JavaScript. That excludes atoms related to pointers and preprocessor directives. Furthermore, we conduct an informal search of programming forums, solutions to Code Golf~\footnote{https://codegolf.stackexchange.com/} problems, code style guidelines, and expert knowledge to identify new atom candidates. Overall, the repeated measures analyzes 24 atoms, 15 from the original study and 9 that are new and specific to JavaScript. Table~\ref{tab:atoms_replication} presents the complete list.

@@

The second section presents the programs, one at a time. For each one, there is a text box where the answer should be written and a ``Next'' button. If the subject leaves the text box empty and presses ``Next'', this is treated as a wrong answer. To reduce the likelihood of a subject attempting to execute the programs, the web application verifies whether the subject tries to change tabs or windows and presents a pop-up message if that is the case. Furthermore, it presents the programs as images, instead of text, to demotivate respondents from resorting to external resources by copying and pasting the code into an interpreter. Upon submitting an answer for a particular program, the subject is automatically led to a similar page, containing the next one.

@@

\subsection{Latin Square Study Setting}\label{sec:meth:survey}

@@

To complement the two experiments, we perform semi-structured interviews with professional JavaScript developers, aiming to identify their perceptions regarding programs containing atoms of confusion (research question RQ2). We also ask each participant if they know of any other JavaScript-specific construct or idiom that they regard as being likely to make the code hard to understand.% (research question RQ3). 
In this section we detail the protocol we followed to conduct the interviews and to analyze the results.

@@

\subsubsection*{Interview Process} We conduct semi-structured interviews using web conferencing software. We record all the interviews with the consent of the participants. On average, the interviews last 26.29 minutes, with the shortest one lasting 14.59 minutes and the longest one 43.06 minutes. Two of the researchers conduct the interviews, and a third one listens to all the recordings to cross-validate the collected data. The interviews have three main parts. In the first one, we ask the developers the following demographic information: name, email, gender, level of education, current job position, JavaScript experience in years, and other programming languages they have worked with. Table \ref{pinterview} summarizes this demographic information.

@@

To understand how often the analyzed atom candidates appear in open source projects, and thus answer our fourth research question (\emph{What is the frequency of occurrence of atoms of confusion in practice?}), we mined a set of GitHub open source repositories. To this end, we first collected the most popular GitHub repositories that are primarily written in JavaScript. We measured popularity using the project's stargazers. This metric, available through the GitHub API, represents the number of stars a project received from users of the platform. The same metric has been used in a number of previous studies as a proxy to estimate a project's popularity~\cite{gyimesi2019bugsjs,canedo:esem2020}. We then selected the top 100 most popular repositories and removed projects that did not reach the first quartile of the distribution of lines of code.

@@

\begin{table}[ht]
  \centering
   \caption{Some descriptive statistics about the projects used in the MSR study}
  \begin{scriptsize}
 \begin{tabular}{rrrrr}
   \hline
                       & Min.             & Median        & Mean             & Max. \\ \hline
 Lines of Code         & \num{5543}       & \num{36161.5} & \num{111432.33}  & \num{1278405} \\
 Num. of Forks         & \num{1244}       & \num{6078}    & \num{8906.24}    & \num{68849} \\
 Num. of Contributors  & \num{6}          & \num{285.5}   & \num{533.44}     & \num{4047} \\
 Num. of Stars         & \num{23672}      & \num{34990}   & \num{46919.51}   & \num{310935} \\

    \hline
 \end{tabular}
 \end{scriptsize}
 \label{tab:projects-statistics} 
 \end{table}

>>>>

\castor{We must have introduced the atoms before.}
The first experiment we perform uses a repeated measures, or within-subject, design~\cite{Keselman:2001:ARM}. This experiment is inspired by the work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, but targeting JavaScript instead of the C language, and including some methodological differences. It covers all the atom candidates analyzed in the work of Gopstein et al. that can be transposed to JavaScript and adds candidates that are specific to JavaScript.
%Overall, we select 24 atom candidates in the repeated measures study.

@@

% The design of the repeated measures study considers two treatments: the presence or absence of atom candidates within the programs.
To identify atom candidates, we start out by selecting every atom candidate from Gopstein's study that can also happen in JavaScript. That excludes atoms related to pointers and preprocessor directives. Furthermore, we conduct an informal search of programming forums, solutions to Code Golf~\footnote{https://codegolf.stackexchange.com/} problems, code style guidelines, and expert knowledge to identify new atom candidates. Overall, the repeated measures analyzes 24 atoms, 15 from the original study and 9 that are new and specific to JavaScript. Table~\ref{tab:atoms_replication} presents the complete list.

@@

The second section presents the programs, one at a time. For each one, there is a text box where the answer should be written and a ``Next'' button. If the subject leaves the text box empty and presses ``Next'', this is treated as a wrong answer. To reduce the likelihood of a subject attempting to execute the programs, the web application verifies whether the subject tries to change tabs or windows and presents a pop-up message if that is the case. Furthermore, it presents the programs as images, instead of text, to demotivate respondents from resorting to external resources by copying and pasting the code into an interpreter. Upon submitting an answer for a particular program, the subject is automatically led to a similar page, containing the next program.

@@

\subsection{Latin Square Study}\label{sec:meth:survey}

@@

To complement the two experiments, we perform semi-structured interviews with professional JavaScript developers, aiming to identify their perceptions regarding programs containing atoms of confusion (research question RQ2). We also ask each participant if they know of any other JavaScript-specific construct or idiom that they regard as being likely to make the code hard to understand. % (research question RQ3). 
 In this section we detail the protocol we followed to conduct the interviews and to analyze the results.

@@

\subsubsection*{Interview Process} We conduct semi-structured interviews using a web conferencing software. We record all the interviews with the consent of the participants. On average, the interviews last 26.29 minutes, with the shortest one lasting 14.59 minutes and the longest one 43.06 minutes. Two of the researchers conduct the interviews, and a third one listens to all the recordings to cross-validate the collected data. The interviews have three main parts. In the first one, we ask the developers the following demographic information: name, email, gender, level of education, current job position, JavaScript experience in years, and other programming languages they have worked with. Table \ref{pinterview} summarizes this demographic information.

@@

To understand how often the analyzed atom candidates appear in open source projects, and thus answer our third research question (\emph{What is the frequency of occurrence of atoms of confusion in practice?}), we mined a set of GitHub open source repositories. To this end, we first collected the most popular GitHub repositories that are primarily written in JavaScript. We measured popularity using the project's stargazers. This metric, available through the GitHub API, represents the number of stars a project received from users of the platform. The same metric has been used in a number of previous studies as a proxy to estimate a project's popularity~\cite{gyimesi2019bugsjs,canedo:esem2020}. We then selected the top 100 most popular repositories and removed projects that did not reach the first quartile of the distribution of lines of code.

@@

\begin{table}[ht]
  \centering
   \caption{Some descriptive statistics about the projects used in the MSR study}
  \begin{scriptsize}
 \begin{tabular}{rrrrr}
   \toprule
                       & Min.             & Median        & Mean             & Max. \\ \midrule
 Lines of Code         & \num{5543}       & \num{36161.5} & \num{111432.33}  & \num{1278405} \\
 Num. of Forks         & \num{1244}       & \num{6078}    & \num{8906.24}    & \num{68849} \\
 Num. of Contributors  & \num{6}          & \num{285.5}   & \num{533.44}     & \num{4047} \\
 Num. of Stars         & \num{23672}      & \num{34990}   & \num{46919.51}   & \num{310935} \\

    \bottomrule
 \end{tabular}
 \end{scriptsize}
 \label{tab:projects-statistics} 
 \end{table}

### 2022-07-25 4_Result.tex
small fixes in the text

%\section{Results of the Survey}
\label{sec:survey-resuts}

@@

\subsubsection*{Exploratory Data Analysis. }
For each of the 24 atom candidates, the participants predicted the outputs of two versions, one clean (control) and one obfuscated (treatment), as per the definition of a repeated measures design~\cite{Hunter-Experimenters}. Thus, each participant examined 48 code snippets.  We also measured the time required by the participants to provide their answers. For most cases, participants made more mistakes when attempting to predict the outcomes of the obfuscated versions.

@@

\begin{table}[tb]
\caption{Summary of the correctness analysis.}
\label{tab:diff-correctness-repeated}
\centering{
\begin{scriptsize}
\begin{tabular}{lccc} \toprule
  Atom & Confusing & Clean & $\Delta$(\%)  \\ \midrule
Type Conversion           &            5.0 &      27.0 &                 +440.0 \\
Change of Literal Encoding &           9.0 &      36.0 &                 +300.0 \\
Comma Operator            &            8.0 &      29.0 &                 +262.0 \\
Object Destructuring      &           15.0 &      42.0 &                 +180.0 \\
Assignment As Value       &           18.0 &      43.0 &                 +139.0 \\
Pre-Increment             &           13.0 &      28.0 &                 +115.0 \\
Post-Increment            &            8.0 &      17.0 &                 +112.0 \\
Array Destructuring       &           15.0 &      28.0 &                 +87.0 \\
Indentation no Braces     &           30.0 &      50.0 &                 +67.0 \\
Omitted Curly Braces      &           35.0 &      51.0 &                 +46.0 \\
Object Spread             &           21.0 &      30.0 &                 +43.0 \\
Array Spread              &           22.0 &      31.0 &                 +41.0 \\
Automatic Semicolon Insertion &       15.0 &      21.0 &                 +40.0 \\
Infix Operator Precedence &           47.0 &      53.0 &                 +13.0 \\
Arrow Function            &           54.0 &      58.0 &                  +7.0 \\
Implicit Predicate        &           41.0 &      44.0 &                  +7.0 \\
Indentation With Braces   &           53.0 &      55.0 &                  +4.0 \\
Conditional Operator      &           60.0 &      62.0 &                  +3.0 \\
Constant Variables        &           59.0 &      61.0 &                  +3.0 \\
Dead Unreachable Repeated &           63.0 &      64.0 &                  +2.0 \\
Repurposed Variables      &           23.0 &      23.0 &                   0.0 \\
Arithmetic as Logic       &           52.0 &      47.0 &                 -10.0 \\
Logic as Control Flow     &           33.0 &      28.0 &                 -15.0 \\
Property Access           &           51.0 &      42.0 &                 -18.0 \\
\bottomrule  
\end{tabular}
\end{scriptsize}
}
\end{table}

@@

Table~\ref{tab:repeated:time} presents the mean and median times required by participants to provide answers. The data is based on the 1648 correct and 1572 incorrect answers collected in the study. Contrary to our intuition, the mean time required by participants to provide an incorrect answer is 25\% greater than the time required to provide a correct one and the median time is 20\%. greater. The standard deviations suggest that there is great variation in the times required by different participants, for different code snippets. Notwithstanding, the standard deviation for incorrect answers is 62.58\% greater when compared to the same statistic for correct answers.

@@

In the latin-square study, we estimate the impact of atoms considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{time} (how long to provide a correct answer). In particular, in the time analysis, differently from the repeated  measures study, we compare the time required by participants to submit a correct response when analyzing code snippets with and without atom candidates. This study is based on the responses of 140 participants (a total of 70 replicas). All participants had taken at least some university course or hold a bachelor degree or equivalent. In addition, 21 participants hold a master's degree and three a doctorate degree. Considering the programming experience of our respondents, 19\% have more than ten years of programming experience, 37\% have between four and ten years of experience, 37\% have between one and four years of experience, and 7\% have less than one year of programming experience.  
Accordingly, we characterize the effect of atoms of confusion in JavaScript code taking into account the perceptions of both novice and experienced developers.

\subsection{Misunderstanding Rate Analysis}
\castor{We need to be uniform about terminology. Are we going with ``misunderstanding rate analysis''? The problem is that it is not clear to me to which rate this refers.}

@@

As mentioned in Section~\ref{sec:meth:survey}, each participant in this study evaluated ten code snippets, from which five were in their confusing versions, whilst the other five contained clean versions of the code snippets (i.e., without the atom candidates). As in the repeated measures study, the participants should provide the expected outcomes of the code snippets. Differently from that study, in this one each participant only predicts the outcome of one version of each code snippet, either clean or obfuscated. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{time}. 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness.

@@

\subsubsection*{Statistical analysis}
We use the non-parametric \emph{Mann-Whitney U test} to
investigate the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of clean and confusing versions of a code snippet.
%, regardless of evaluating the confusing or clean version of the code.
The results of Table~\ref{tab:difference-time-taken}
suggest that we should refute the null hypotheses for five atom candidates (Comma Operator, Implicit Predicate, Logic as Control Flow, Pre-Increment, and Arithmetic as Logic), after applying the Benjamini-Hochberg correction with a false discovery rate of 5\%. For the first three, the analysis suggests that the participants need more time to predict the outcome of the code snippet in the confusing code version. For the atom candidates Arithmetic as Logic and Pre-Increment, the participants take less time to predict the outcome of the code snippets in the confusing version. We also computed the effect size using Cliff's Delta statistic. In the table, negative effect sizes suggest that it took less time to correctly predict the output of clean versions of the snippets.  Considering the thresholds established by Romano et al.~\cite{Romano:2006:ASO} (0.147 $<$ $|$d$|$ $<$ 0.33 small, $|$d$|$ $<$ 0.474 medium, otherwise large), we found a large effect for the Comma Operator atom candidate; a medium effect size for Logic as Control Flow, and small effect sizes for Automatic Semicolon Insertion, Implicit Predicate, Arithmetic as Logic, Post-, and Pre-Increment.

@@

In this section we present the results of the interviews with the practitioners. We contrast the findings presented in Section~\ref{sec:survey-resuts} with the opinion of software developers about their preferences regarding the confusing or clean versions of the code snippets we used in our experiment. For the interview study, we only considered atoms that were analyzed in both the repeated measures (Section~\ref{sec:repeated}) and the latin square (Section~\ref{sec:latin}) studies.

@@

The Pre-Increment atom candidate also caused such
divide in one of the interviewees, who
regarded the clean version as simpler to understand, but would still opt to write
code with the atom. In contrast, %to such opinion,
one of the participants found the version with the atom candidate more elegant, but recognized it was less readable, and was willing to sacrifice elegance for readability. In the repeated measures study, we found a significant difference in favor of the clean version, with a large effect size in its favor. In the latin square study, no difference could be observed in terms of correctness. However, there was a significant difference in terms of the time required predict the output correctly in favor of the obfuscated version. This highlights how factors such as the experience of the participants and the selection of code snippets can have considerable impact on the results of studies about code readability~\cite{Feitelson:2021:CPC}.
\castor{Should the last sentence above be in the discussion?}

%% \rb{pela discuss\~{a}o anterior, parece-me que alguns
%%   desenvolvedores reconhecem que esses candidatos
%%   a \'{a}tomos introduzem certa dificuldade de compreens\~{a}o;
%%   mas mesmo assim optam por usar a constru\c c\~{a}o correspondente.
%%   Acho que cabe um box aqui com essa discuss\~{a}o sobre isso.}

@@

Considering all JavaScript projects in our dataset, we found a total of \num{364873} atom candidates, though four atoms are responsible
for 92.97\% of this total: Implicit Predicate, Post Increment, Conditional Operator, and Omitted Curly Braces. The first two, based on the results of Section~\ref{sec:survey-resuts}, can be considered atoms of confusion. The remaining atom
candidates comprise \num{25621} occurrences combined, 7.03\% of the total number of occurrences.
The Comma Operator and Arithmetic as Logic atoms are the ones that arise less
frequently (0.001\% in total with 232 and 165 occurrences, respectively).

>>>>

%\section{Results of the Survey}
%\label{sec:survey-resuts}

@@

\subsubsection*{Exploratory Data Analysis}
For each of the 24 atom candidates, the participants predicted the outputs of two versions, one clean (control) and one obfuscated (treatment), as per the definition of a repeated measures design~\cite{Hunter-Experimenters}. Thus, each participant examined 48 code snippets.  We also measured the time required by the participants to provide their answers. For most cases, participants made more mistakes when attempting to predict the outcomes of the obfuscated versions.

@@

\begin{table}[tb]
\caption{Summary of the correctness analysis.}
\label{tab:diff-correctness-repeated}
\centering{
\begin{scriptsize}
\begin{tabular}{lccc} \toprule
  Atom & Confusing & Clean & $\Delta$(\%)  \\ \midrule
Type Conversion           &            5 &      27 &                 +440 \\
Change of Literal Encoding &           9 &      36 &                 +300 \\
Comma Operator            &            8 &      29 &                 +262 \\
Object Destructuring      &           15 &      42 &                 +180 \\
Assignment As Value       &           18 &      43 &                 +139 \\
Pre-Increment             &           13 &      28 &                 +115 \\
Post-Increment            &            8 &      17 &                 +112 \\
Array Destructuring       &           15 &      28 &                 +87 \\
Indentation no Braces     &           30 &      50 &                 +67 \\
Omitted Curly Braces      &           35 &      51 &                 +46 \\
Object Spread             &           21 &      30 &                 +43 \\
Array Spread              &           22 &      31 &                 +41 \\
Automatic Semicolon Insertion &       15 &      21 &                 +40 \\
Infix Operator Precedence &           47 &      53 &                 +13 \\
Arrow Function            &           54 &      58 &                  +7 \\
Implicit Predicate        &           41 &      44 &                  +7 \\
Indentation With Braces   &           53 &      55 &                  +4 \\
Conditional Operator      &           60 &      62 &                  +3 \\
Constant Variables        &           59 &      61 &                  +3 \\
Dead Unreachable Repeated &           63 &      64 &                  +2 \\
Repurposed Variables      &           23 &      23 &                   0 \\
Arithmetic as Logic       &           52 &      47 &                 -10 \\
Logic as Control Flow     &           33 &      28 &                 -15 \\
Property Access           &           51 &      42 &                 -18 \\
\bottomrule  
\end{tabular}
\end{scriptsize}
}
\end{table}

@@

Table~\ref{tab:repeated:time} presents the mean and median times required by the participants to provide answers. The data is based on the 1648 correct and 1572 incorrect answers collected in the study. Contrary to our intuition, the mean time required by participants to provide an incorrect answer is 25\% greater than the time required to provide a correct one and the median time is 20\% greater. The standard deviations suggest that there is great variation in the times required by different participants, for different code snippets. Notwithstanding, the standard deviation for incorrect answers is 62.58\% greater when compared to the same statistic for correct answers.

@@

In the latin-square study, we estimate the impact of atoms considering the same two perspectives of the previous experiment: \emph{correctness} (number of wrong answers)
and \emph{time} (how long to provide a correct answer). In particular, in the time analysis, differently from the repeated  measures study, we compare the time required by participants to submit a correct response when analyzing code snippets with and without atom candidates. This study is based on the responses of 140 participants (a total of 70 replicas). All participants had taken at least some university course or hold a bachelor degree or equivalent. In addition, 21 participants hold a master's degree and three a doctorate degree. Considering the programming experience of our respondents, 19\% have more than ten years of programming experience, 37\% have between four and ten years of experience, 37\% have between one and four years of experience, and 7\% have less than one year of programming experience.  
Accordingly, we characterize the effect of atoms of confusion in JavaScript code taking into account the perceptions of both novice and experienced developers.

\subsection{Correctness Analysis}
% \castor{We need to be uniform about terminology. Are we going with ``misunderstanding rate analysis''? The problem is that it is not clear to me to which rate this refers.}

@@

As mentioned in Section~\ref{sec:meth:survey}, each participant in this study evaluated ten code snippets, from which five were in their confusing versions, whilst the other five contained clean versions of the code snippets (i.e., without the atom candidates). As in the repeated measures study, the participants should provide the expected outcomes of the code snippets. Differently from that study, in this one each participant only predicts the outcome of one version of each code snippet, either clean or obfuscated. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{time}. 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the correctness experiment.

@@

\subsubsection*{Statistical analysis}
We use the non-parametric \emph{Mann-Whitney U test} to
investigate the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of clean and confusing versions of a code snippet.
%, regardless of evaluating the confusing or clean version of the code.
The results of Table~\ref{tab:hypothesis-testing}
suggest that we should refute the null hypotheses for five atom candidates (Comma Operator, Implicit Predicate, Logic as Control Flow, Pre-Increment, and Arithmetic as Logic), after applying the Benjamini-Hochberg correction with a false discovery rate of 5\%. For the first three, the analysis suggests that the participants need more time to predict the outcome of the code snippet in the confusing code version. For the atom candidates Arithmetic as Logic and Pre-Increment, the participants take less time to predict the outcome of the code snippets in the confusing version. We also computed the effect size using Cliff's Delta statistic. In the table, negative effect sizes suggest that it took less time to correctly predict the output of clean versions of the snippets.  Considering the thresholds established by Romano et al.~\cite{Romano:2006:ASO} (0.147 $<$ $|$d$|$ $<$ 0.33 small, $|$d$|$ $<$ 0.474 medium, otherwise large), we found a large effect for the Comma Operator atom candidate; a medium effect size for Logic as Control Flow, and small effect sizes for Automatic Semicolon Insertion, Implicit Predicate, Arithmetic as Logic, Post-, and Pre-Increment.

@@

In this section we present the results of the interviews with the practitioners. We contrast the findings presented in Section~\ref{sec:latin} and Section~\ref{sec:repeated} with the opinion of software developers about their preferences regarding the confusing or clean versions of the code snippets we used in our experiment. For the interview study, we only considered atoms that were analyzed in both the repeated measures (Section~\ref{sec:repeated}) and the latin square (Section~\ref{sec:latin}) studies.

@@

The Pre-Increment atom candidate also caused such
divide in one of the interviewees, who
regarded the clean version as simpler to understand, but would still opt to write
code with the atom. In contrast, %to such opinion,
one of the participants found the version with the atom candidate more elegant, but recognized it was less readable, and was willing to sacrifice elegance for readability. In the repeated measures study, we found a significant difference in favor of the clean version, with a large effect size in its favor. In the latin square study, no difference could be observed in terms of correctness. However, there was a significant difference in terms of the time required to predict the output correctly in favor of the obfuscated version. This highlights how factors such as the experience of the participants and the selection of code snippets can have considerable impact on the results of studies about code readability~\cite{Feitelson:2021:CPC}.
\castor{Should the last sentence above be in the discussion?}
\rb{Agree. We can move it to the discussion section.}
%% \rb{pela discuss\~{a}o anterior, parece-me que alguns
%%   desenvolvedores reconhecem que esses candidatos
%%   a \'{a}tomos introduzem certa dificuldade de compreens\~{a}o;
%%   mas mesmo assim optam por usar a constru\c c\~{a}o correspondente.
%%   Acho que cabe um box aqui com essa discuss\~{a}o sobre isso.}

@@

Considering all JavaScript projects in our dataset, we found a total of \num{364873} atom candidates, though four atoms are responsible
for 92.97\% of this total: Implicit Predicate, Post Increment, Conditional Operator, and Omitted Curly Braces. The first two, based on the results of Section~\ref{sec:latin} and Section~\ref{sec:repeated}, can be considered atoms of confusion. The remaining atom
candidates comprise \num{25621} occurrences combined, 7.03\% of the total number of occurrences.
The Comma Operator and Arithmetic as Logic atoms are the ones that arise less
frequently (0.001\% in total with 232 and 165 occurrences, respectively).

### 2022-07-25 discussion.tex
small fixes in the text

\begin{mh}
  {\bf Answer to RQ1:} The first study (survey) gives evidence that some of the atom candidates in \clang and \cpplang programs that also exist in JavaScript correspond to a source of misunderstanding in
  JavaScript code. 
\end{mh}

@@

\begin{mh}
  {\bf Answer to RQ2:} The qualitative analysis of the
  interviews supports the results of the first study,
  since JavaScript developers most often agree that atoms of confusion compromise
  source code understanding. 
\end{mh}

@@

\begin{mh}
  {\bf Answer to RQ3:} The MSR study reveals that
  the several atom candidates explored in our research
  appear frequently in practice, and cleaning up the use of 
  Post-Increment/Decrement and the Automatic Semicolon Insertion
  might improve the readabiliy of JavaScript code substantially. 
\end{mh}

>>>>

\begin{mh}
  {\bf Answer to RQ1:} Our experiments using repeated measures and the Latin square designs give evidence that some of the atom candidates in \clang and \cpplang programs that also exist in JavaScript correspond to a source of misunderstanding in
  JavaScript code. 
\end{mh}

@@

\begin{mh}
  {\bf Answer to RQ2:} The qualitative analysis of the
  interviews supports the results of our experiments---
  JavaScript developers most often agree that atoms of confusion compromise
  source code understanding. 
\end{mh}

@@

\begin{mh}
  {\bf Answer to RQ3:} The MSR study reveals that
  several atom candidates explored in our research
  appear frequently in practice, and cleaning up the use of 
  Post-Increment/Decrement and the Automatic Semicolon Insertion
  might improve the readabiliy of JavaScript code substantially. 
\end{mh}
